---
title: Normal Right Tail Area
params:
    mu: 42
    sigma: 12
    x: 53
---

```{r}
#| echo: false
mu<-params$mu
x<-params$x
sigma<-params$sigma
z<-(x-mu)/sigma

rounded_z <- round(z, 2)
area <- 1.0-pnorm(z)
rounded_area <- round(area, 4)
nearest_percent <- round(area*100)
str_area <- sprintf("%.10f", area)
str_rounded_area<-sprintf("%.4f", rounded_area)
```

We have $x = `r x`$, $\mu = `r mu`$, and $\sigma = `r sigma`$ . We want to find the chance of $x$ being greater than $`r x`$ in this situation.

Here is a rough picture of the area we want. Its the shaded area to the right of $x=`r x`$: 

```{r}
#| echo: false
graph_url<-paste0("https://statplosion-api-x5isouofzq-uk.a.run.app/righttail")
params_str<-paste0("x=",x,"&","mu=",mu,"&","sigma=",sigma)
graph_url<-paste0(graph_url,"?", params_str)
```

![Right tail area for $x=`r x`$, $\mu=`r mu`$, and $\sigma=`r sigma`$](`r graph_url`)

Our approach will be to find the z-value from the given info, then use
**1.0-NORMSDIST** to calculate the right tail area using a spreadsheet.

This works because the area above is the same as the right tail area using 
the $z$-value we get for $x=`r x`$:

```{r, child='calculate_z_value.Rmd'}
```

- Now use the **1.0-NORMSDIST** function using the $z$ we just found

|     |    column A    |    column B    |    column C    |    
|-----|----------------|----------------|----------------|
|  1  |                |                |                | 
|  2  |      x         |   `r x`        |                |
|  3  |      mu        |   `r mu`       |                |
|  4  |      sigma     |   `r sigma`    |                |
|  5  |      z         |   `r z`        |                |
|  6  |    right area  | =1.0-NORMSDIST(B5) |            |
|  7  |                |                |                |

- The result is this 

|     |    column A    |    column B    |    column C    |   
|-----|----------------|----------------|----------------|
|  1  |                |                |                |
|  2  |      x         |   `r x`        |                |
|  3  |      mu        |   `r mu`       |                |
|  4  |      sigma     |   `r sigma`    |                |
|  5  |      z         |   `r z`        |                |
|  6  |   right area   |   `r area`     |                |
|  7  |                |                |                |

To four decimal places this is $`r str_rounded_area`$

Sometimes we like to have it to the nearest percent and for that we have 
$`r nearest_percent`\%$.
